---
title: "R Notebook"
output: default
---
# TODO add setup 

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
source("R/CBI_mapCreation.R")
theme_set(mxblsdl)

library(data.table) # data structure
library(tidyverse)
library(ggridges) # additional ridge plotting
library(ggplot2) # plotting
library(sf)
```

# Setup

```{r}
# set functional unit
# funit <- "MTrecovered"
funit <- "kWh"
```

# Load Data

First find the model results which are classified by the 'metric', either kWh or MT Recovered. Using MT Recovered per Kevin's email.

Using `MTrecovered` as the functional unit. This may change to be functional unit `kWh` as well.
```{r include=TRUE}
# find all results files
files <- dir(glue::glue("CBREC_Model_Output/{funit}"), full.names = T, recursive = T)

sf_path <- dir("CBREC-LCA_timber_activity_polygons_2016-2019", pattern = ".shp$", full.names = T)
harvests <- read_sf(sf_path)
```

## Scenario data

This includes the scenario pairings and the scenario IDs

```{r}
scenario_paths <- dir("inst", full.names = T)

scen_pairings <- fread(scenario_paths[1])
scen_mat <- fread(scenario_paths[2])

# remove pulp market
scen_mat[, Pulp_Market := NULL]
```

# Prepare Data for maps 4-8

```{r}
ids <- scenario_function(scenario_matrix = scen_mat,
                  piled = 50,
                  use_collection = "All Tech Recoverable",
                  use_burn = "None",
                  ref_burn = "None", 
                  negate_ref = T)
# special reference for Rx purn

# filter by reference ID
data <- lapply(files, function(file) {
  dat <- readRDS(file)
  da <- dat[grepl(paste0("\\b", ids[["ref_id"]], "\\b", collapse = "|"), names(dat))]
  return(da)
})
# filter by Use ID
data <- lapply(data, function(d) {
  da <- d[grepl(paste0("\\b", ids[["use_id"]], "\\b", collapse = "|"), names(d))]
  return(da)
})

# simplify list structure
data <- unlist(data, recursive = F)

# Missing SOX NEED TO EMAIL ABOUT
out <- lapply(data, function(d) {
  vals <- d$time_series[, .(net.CH4_MTperkWh,
                            net.N2O_MTperkWh,
                            net.PM2.5_MTperkWh,
                            # Missing SOX
                            MT_Residue_Mobilized, 
                            MT_Residue_Mobilized_perAcre)] %>%
    slice(1)
  return(vals)
})

# bind together
data <- rbindlist(out)
```

Paste polygon number into
```{r}
poly_num <- tools::file_path_sans_ext(gsub(".*/", "", unlist(files)))

data[["poly_num"]] <- poly_num
```

# Spatial Join

```{r}
# rename ID for join
harvests <- harvests %>%
      rename(poly_num = OBJECTID) %>%
      mutate(poly_num = as.character(poly_num))

# join by polygon ID
data <- left_join(data, harvests, by = "poly_num")
```


Change the units if the functional unit is kWh. The final units should be kg / MWh
```{r}
if(funit == "kWh") {
  data <- data %>%
    mutate(N2O_kg = net.N2O_MTperkWh * 1000000, # converting MT to kg and kWh to MWh
           CH4_kg = net.CH4_MTperkWh * 1000000,
           PM25_kg = net.PM2.5_MTperkWh * 1000000)
}
```

## Output

Prepare the histograms
```{r}
# string designating reference scenario
  t = "Prescription Burn"

if(funit == "MTrecovered") {
  # NOTE need to change xaxis label expression
  ch4 <- data %>% 
    filter(net.CH4_MTperMT_Mobilized < quantile(.$net.CH4_MTperMT_Mobilized, .99)) %>% 
    ggplot(aes(x = net.CH4_MTperMT_Mobilized, fill = ..x..)) +
    theme_minimal() +
    geom_histogram(binwidth = .0001, show.legend = F) +
    scale_fill_gradient(low = "#63B8FF", high = "#CD950C") +
    labs(title = glue::glue("{t} Counterfactul"),
         x = expression("MT CH"[4]~" per MT Recovered"),
         y = "Count") +
    theme(text = element_text(size = 16))
  
  n2o <- data %>% 
    filter(net.N2O_MTperMT_Mobilized < quantile(.$net.N2O_MTperMT_Mobilized, .99)) %>% 
    ggplot(aes(x = net.N2O_MTperMT_Mobilized, fill = ..x..)) +
    theme_minimal() +
    geom_histogram(binwidth = .000001, show.legend = F) +
    scale_fill_gradient(low = "#63B8FF", high = "#CD950C") +
    labs(title = glue::glue("{t} Counterfactul"),
         x = expression("MT N"[2]~"O per MT Recovered"),
         y = "Count") +
    theme(text = element_text(size = 16))
  
  pm25 <- data %>% 
    filter(net.PM2.5_MTperMT_Mobilized < quantile(.$net.PM2.5_MTperMT_Mobilized, .99)) %>% 
    ggplot(aes(x = net.PM2.5_MTperMT_Mobilized, fill = ..x..)) +
    theme_minimal() +
    geom_histogram(binwidth = .0001, show.legend = F) +
    scale_fill_gradient(low = "#63B8FF", high = "#CD950C") +
    labs(title = glue::glue("{t} Counterfactul"),
         x = expression("MT PM 2.5 per MT Recovered"),
         y = "Count") +
    theme(text = element_text(size = 16))  
} else {
  # NOTE need to change xaxis label expression
  ch4 <- data %>% 
    filter(CH4_kg < quantile(.$CH4_kg, .99)) %>% 
    ggplot(aes(x = CH4_kg, fill = ..x..)) +
    theme_minimal() +
    geom_histogram(binwidth = .05, show.legend = F) +
    scale_fill_gradient(low = "#63B8FF", high = "#CD950C") +
    labs(title = glue::glue("{t} Counterfactul"),
         x = expression("MT CH"[4]~" per MT kWh"),
         y = "Count") +
    theme(text = element_text(size = 16))

n2o <- data %>% 
    filter(N2O_kg < quantile(.$N2O_kg, .99)) %>% 
    ggplot(aes(x = N2O_kg, fill = ..x..)) +
    theme_minimal() +
    geom_histogram(binwidth = .001, show.legend = F) +
    scale_fill_gradient(low = "#63B8FF", high = "#CD950C") +
    labs(title = glue::glue("{t} Counterfactul"),
         x = expression("MT N"[2]~"O per MT kWh"),
         y = "Count") +
    theme(text = element_text(size = 16))

pm25 <- data %>% 
    filter(PM25_kg < quantile(.$PM25_kg, .99)) %>% 
    ggplot(aes(x = PM25_kg, fill = ..x..)) +
    theme_minimal() +
    geom_histogram(binwidth = .08, show.legend = F) +
    scale_fill_gradient(low = "#63B8FF", high = "#CD950C") +
    labs(title = glue::glue("{t} Counterfactul"),
         x = expression("MT PM 2.5 per MT kWh"),
         y = "Count") +
    theme(text = element_text(size = 16))
}
```

# Write out plot

```{r}
ggsave(plot = ch4, filename = glue::glue("plots/ch4_{funit}.png"),
       height = 7,
       width = 12,
       dpi = 400)

ggsave(plot = n2o, filename = glue::glue("plots/n2o_{funit}.png"),
       height = 7,
       width = 12,
       dpi = 400)

ggsave(plot = pm25, filename = glue::glue("plots/pm25_{funit}.png"),
       height = 7,
       width = 12,
       dpi = 400)
```

Write the layers to Qgis
```{r}
write_sf(data, 
         glue::glue("Q/input/harvests_{funit}.gpkg"),
         layer = "criteriants",
         delete_layer = T)
```

# check layers
```{r}
st_layers(glue::glue("Q/input/harvests_{funit}.gpkg"))
```


## TODO
Need to add in the code to generate the ten year averages...
