---
title: "CBREC LCA Analysis of Timber Harvest Projects from 2016 - 2019"
author: "Max Blasdel"
date: "August 11, 2020"
output:
  html_document: default
---

# Purpose

Create final maps from CBREC outputs for use in results report

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

Load libraries and helper functions

```{r results='hide', message = F}
#source("R/CBI_postFunctions.R")
source("R/CBI_mapCreation.R")

library(data.table) # data structure
library(tidyverse)
library(ggridges) # additional ridge plotting
library(ggplot2) # plotting
library(sf)
```

Define helper functions

```{r include=TRUE}
# set the theme for all plots
theme_set(mxblsdl)
```

# Setup

Set user defined variables

## Define Scenarios

These are variables that set the definition of the scenario. I could move the functional unit into this

```{r}
#ref_scen <- "Pile and Broadcast"
ref_scen <- "None"

# set functional unit
# funit <- "MTrecovered"
funit <- "kWh"
```

# Load Data

## Model outputs

First find the model results which are classified by the 'metric', either kWh or MT Recovered. Using MT Recovered per Kevin's email.

Using `MTrecovered` as the functional unit. This may change to be functional unit `kWh` as well.
```{r include=TRUE}
# find all results files
files <- dir(glue::glue("CBREC_Model_Output/{funit}"), full.names = T, recursive = T)
length(files)
# find files which are larger than a certain size and have data
```

## Spatial Data

These are timber harvests from all years

```{r}
sf_path <- dir("CBREC-LCA_timber_activity_polygons_2016-2019", pattern = ".shp$", full.names = T)
harvests <- read_sf(sf_path)
```

## Scenario data

This includes the scenario pairings and the scenario IDs

```{r}
scenario_paths <- dir("inst", full.names = T)

scen_pairings <- fread(scenario_paths[1])
scen_mat <- fread(scenario_paths[2])

# remove pulp market
scen_mat[, Pulp_Market := NULL]
```

Define the use and reference scenarios It would be good to make a function here since this will be run a number of times...

This function is what changes based on the map specifications.

```{r}
ids <- scenario_function(scenario_matrix = scen_mat,
                  piled = 50,
                  use_collection = "All Tech Recoverable",
                  use_burn = "None",
                  ref_burn = ref_scen)

poly_num <- tools::file_path_sans_ext(gsub(".*/", "", unlist(files)))
```

# Read the output data and filter based on the scenarios

Data is structured in a list format only showing the time series emissions. I need to filter based on the Use first and then reference. The net emissions for each category are shown in the name of the list. 

```{r include=TRUE}
# Read and filter based on reference ids first
data <- lapply(files, function(file) {
  dat <-
    readRDS(file)
  # get polygon number
  poly_num <- tools::file_path_sans_ext(gsub(".*/", "", unlist(file)))

  da <- dat[grepl(paste0("\\b", ids[["ref_id"]], "\\b", collapse = "|"), names(dat))]
  
  # attach polygon number
  #da[["poly_num"]] <- poly_num
  return(da)
})

# each list should be length one

## May not need this second filter
# Further filter based on selected use case
data <-
  lapply(data, function(file) {
    file[grepl(paste0("\\b", ids[["use_id"]], "\\b",collapse = "|"), names(file))]
  })

# simplify list structure
data <- unlist(data, recursive = F)
```

# Extract important information from data

Bind the polygon number to the values as well. The polygon number or `poly_num` will be used to join the spatial data.

```{r}
out <- lapply(data, function(d) {
  # AGWP and AGTP are both the same for every year of the time series
  vals <- d$time_series[, .(net.MT_CO2e.AGWP.100yr, net.MT_CO2e.AGTP.100yr, MT_Residue_Mobilized, MT_Residue_Mobilized_perAcre)] %>%
    distinct()
  
  return(vals)
})

# bind together
data <- rbindlist(out)
```

Bind polygon number onto data

```{r}
# get polygon number
poly_num <- tools::file_path_sans_ext(gsub(".*/", "", unlist(files)))

data[["poly_num"]] <- poly_num
```

# Bind with spatial data

```{r}
# TODO check on units
# convert data to correct units; This is the difference between MT and grams
if(funit == "kWh") {
  data <-data %>%
    mutate(AGTP_co2e_kg = net.MT_CO2e.AGTP.100yr * 1000000, # converting MT to kg and kWh to MWh
           AGWP_co2e_kg = net.MT_CO2e.AGWP.100yr * 1000000)
}

# rename ID for join
harvests <- harvests %>%
      rename(poly_num = OBJECTID) %>%
      mutate(poly_num = as.character(poly_num))

# join by polygon ID
data <- left_join(data, harvests, by = "poly_num")
```

# Filter data based on criteria
Data not being filtered for the maps, but it is being filtered for the histograms
```{r}
# filtered_data <- data %>% 
#   filter(MT_Residue_Mobilized >= 1)
```

# Plotting

## Historgram with nice gradient

```{r}
t <- ifelse(ref_scen == "None", "No Burn", "Pile and Broadcast")

# choose metric
#v <- 'net.MT_CO2e.AGTP.100yr' # needs some manual garbage right now
v <- 'net.MT_CO2e.AGWP.100yr'

if(funit == "MTrecovered") {
  g <- data[get(v) < quantile(data[[v]], .97), ] %>% 
  ggplot(aes(x = get(v), fill = ..x..)) +
  theme_minimal() +
  geom_histogram(binwidth = .002, show.legend = F) +
  scale_fill_gradient(low = "#63B8FF", high = "#CD950C") +
  labs(title = glue::glue("{t} Counterfactul"),
       x = expression("MT CO"[2]~"e per MT Recovered"), # dang expression...
       y = "Count") +
  theme(text = element_text(size = 16))  
} else { # is kWh
  # change v since its a different metric for this functional unit
  v <- ifelse(v == "net.MT_CO2e.AGWP.100yr", 'AGWP_co2e_kg', 'AGTP_co2e_kg')
  
  g <- data[get(v) < quantile(data[[v]], .98), ] %>% 
  ggplot(aes(x = get(v), fill = ..x..)) +
  theme_minimal() +
  geom_histogram(binwidth = 4, show.legend = F) +
  scale_fill_gradient(low = "#63B8FF", high = "#CD950C") +
  labs(title = glue::glue("{t} Counterfactul"),
       x = expression("kg CO"[2]~"e per MWh"), # dang expression...
       y = "Count") +
  theme(text = element_text(size = 16))  
}
g
```

# Write out plot

Needs Reference scenario, functional unit, and specific metric
```{r}
# Get metric
metric <- gsub("net.MT_CO2e.", "", v) %>% 
  gsub(".100yr", "", .)

ggsave(plot = g, filename = glue::glue("plots/co2e/{t}_{funit}_{metric}.png"),
       height = 7,
       width = 12,
       dpi = 400)
```

# Write for use in QGIS

Need both reference scenarios
```{r}
write_sf(data, 
         glue::glue("Q/input/harvests_{funit}.gpkg"),
         layer = ref_scen,
         delete_layer = T)
```

Check on what layers already exist
```{r}
st_layers(glue::glue("Q/input/harvests_{funit}.gpkg"))
```

